---
title: "Group document"
format: html
editor: visual
---

## Quarto

One section for each member of the group

## Romane

```{r}
print("hello world")
```

## Cora

First we created a long data frame from the data, by specifying a 'gene' column. This results in a data frame with 3 column: early_metastasis, gene, log2_expr_level.

```{r}
gravier_clean_aug_long <- gravier_clean_aug |> 
  pivot_longer(
    cols = -c(early_metastasis),
    names_to = 'gene',
    values_to = 'log2_expr_level'
  )
```

## New Features

```{r}
print('Hello, its me!')
```

## Francesc

Hi

```{r}
3*3
```

```{r}
2+2
```

### New Feature

TEST TEST

```{r}
print("Hello!")
```

```{r}
2/2
```

## Louis

Some plot about meta data on covid

```{r}
library(tidyverse)

meta_data <- read_csv("data/subject-metadata.csv",
                      na = c("","N/A","NA"))

meta_data |> 
  drop_na(Cohort, Gender) |> 
  count(Cohort, Gender) |> 
  ggplot(aes(x = Cohort,
             y = n,
             fill = Gender)) +
  geom_col(position = position_dodge(preserve = "single"),
           alpha = 0.5,
           color = "black",
           linewidth = 0.5) +  # side by side
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(
          angle = 30,
          hjust = 1
        )) +
  labs(title = "Type of Covid per gender",
       x = "Cohort",
       y = "n")

```

## New feature

```{r}
print(2+2+2)
```

## Maxence

This is a test

```{r}

sum <- 2+2

```

## New feature (from Max)

We're gonna import some libraries

```{r}

library(tidyverse)
library(ggrepel)
```
